---
title: "Dashboard Analisis Data SOVI (Social Vulnerability Index)"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
# Load pustaka fungsi
source("pustaka_fungsi.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
# UI Dashboard
ui <- dashboardPage(
  skin = "blue",
  
  # Header
  dashboardHeader(
    title = "SOVI Analytics Dashboard",
    titleWidth = 300
  ),
  
  # Sidebar
  dashboardSidebar(
    width = 300,
    sidebarMenu(
      id = "sidebar",
      
      # Data Source Info
      div(class = "sidebar-header", style = "padding: 15px; border-bottom: 1px solid #eee;",
          h4("Data Source", style = "color: #333; margin: 0;"),
          p("Social Vulnerability Index", style = "color: #666; font-size: 12px; margin: 5px 0 0 0;")
      ),
      
      # Menu Items
      menuItem("ðŸ  Dashboard", tabName = "dashboard", icon = icon("tachometer-alt")),
      menuItem("ðŸ“Š Data Overview", tabName = "overview", icon = icon("table")),
      menuItem("ðŸ” Exploratory Analysis", tabName = "exploration", icon = icon("search")),
      menuItem("ðŸ“ˆ Statistical Analysis", tabName = "statistics", icon = icon("chart-line")),
      menuItem("ðŸŽ¯ Advanced Analytics", icon = icon("brain"),
               menuSubItem("PCA Analysis", tabName = "pca"),
               menuSubItem("Cluster Analysis", tabName = "cluster"),
               menuSubItem("Correlation Analysis", tabName = "correlation")
      ),
      menuItem("ðŸ“‹ Reports", tabName = "reports", icon = icon("file-alt")),
      
      # Data Status
      div(class = "sidebar-footer", style = "position: absolute; bottom: 20px; left: 20px; right: 20px;",
          div(id = "data-status", class = "alert alert-info", style = "margin: 0; padding: 10px; font-size: 12px;",
              "Loading data...",
              br(),
              div(class = "progress progress-xs", style = "margin: 5px 0;",
                  div(class = "progress-bar progress-bar-striped active", 
                      style = "width: 100%; animation: progress-bar-stripes 2s linear infinite;")
              )
          )
      )
    )
  ),
  
  # Body
  dashboardBody(
    # Custom CSS
    get_modern_css(),
    
    # Loading overlay
    div(id = "loading-overlay", 
        style = "position: fixed; top: 0; left: 0; width: 100%; height: 100%; background: rgba(255,255,255,0.9); z-index: 9999; display: flex; align-items: center; justify-content: center;",
        div(class = "spinner"),
        div(style = "margin-left: 20px; font-size: 16px; color: #666;", "Loading SOVI data...")
    ),
    
    # Tab Items
    tabItems(
      # Dashboard Tab
      tabItem(tabName = "dashboard",
        fluidRow(
          column(12,
            h1("Social Vulnerability Index (SOVI) Analytics", 
               style = "color: #1e293b; font-weight: 600; margin-bottom: 30px;")
          )
        ),
        
        # Key Metrics
        fluidRow(
          column(3, withSpinner(valueBoxOutput("total_districts"))),
          column(3, withSpinner(valueBoxOutput("avg_poverty"))),
          column(3, withSpinner(valueBoxOutput("avg_population"))),
          column(3, withSpinner(valueBoxOutput("data_completeness")))
        ),
        
        # Charts Row
        fluidRow(
          column(6,
            box(title = "Poverty Rate Distribution", status = "primary", solidHeader = TRUE, width = NULL,
                withSpinner(plotlyOutput("poverty_dist_plot"))
            )
          ),
          column(6,
            box(title = "Population vs Poverty", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(plotlyOutput("pop_poverty_plot"))
            )
          )
        ),
        
        # Map and Summary
        fluidRow(
          column(8,
            box(title = "Geographic Distribution", status = "success", solidHeader = TRUE, width = NULL,
                withSpinner(leafletOutput("sovi_map", height = "400px"))
            )
          ),
          column(4,
            box(title = "Dataset Information", status = "warning", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("dataset_info"))
            )
          )
        )
      ),
      
      # Data Overview Tab
      tabItem(tabName = "overview",
        fluidRow(
          column(12,
            h2("Data Overview", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "SOVI Dataset", status = "primary", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("sovi_table"))
            )
          )
        ),
        
        fluidRow(
          column(6,
            box(title = "Variable Descriptions", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("variable_descriptions"))
            )
          ),
          column(6,
            box(title = "Data Summary Statistics", status = "success", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("summary_stats"))
            )
          )
        )
      ),
      
      # Exploratory Analysis Tab
      tabItem(tabName = "exploration",
        fluidRow(
          column(12,
            h2("Exploratory Data Analysis", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(4,
            box(title = "Analysis Controls", status = "primary", solidHeader = TRUE, width = NULL,
                selectInput("explore_variable", "Select Variable:", choices = NULL),
                selectInput("plot_type", "Plot Type:", 
                           choices = c("Histogram" = "histogram", 
                                     "Box Plot" = "boxplot",
                                     "Density Plot" = "density",
                                     "Violin Plot" = "violin")),
                checkboxInput("show_outliers", "Show Outliers", value = TRUE),
                downloadButton("download_plot", "Download Plot", class = "btn-success")
            )
          ),
          column(8,
            box(title = "Visualization", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(plotlyOutput("exploration_plot", height = "400px"))
            )
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "Statistical Summary", status = "warning", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("variable_summary"))
            )
          )
        )
      ),
      
      # Statistical Analysis Tab
      tabItem(tabName = "statistics",
        fluidRow(
          column(12,
            h2("Statistical Analysis", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(4,
            box(title = "Test Configuration", status = "primary", solidHeader = TRUE, width = NULL,
                selectInput("test_type", "Statistical Test:",
                           choices = c("Normality Test" = "normality",
                                     "Correlation Test" = "correlation",
                                     "T-Test" = "ttest")),
                conditionalPanel(
                  condition = "input.test_type == 'normality'",
                  selectInput("norm_variable", "Select Variable:", choices = NULL)
                ),
                conditionalPanel(
                  condition = "input.test_type == 'correlation'",
                  selectInput("corr_var1", "Variable 1:", choices = NULL),
                  selectInput("corr_var2", "Variable 2:", choices = NULL)
                ),
                conditionalPanel(
                  condition = "input.test_type == 'ttest'",
                  selectInput("ttest_variable", "Test Variable:", choices = NULL),
                  numericInput("ttest_mu", "Test Value (Î¼):", value = 0)
                ),
                actionButton("run_test", "Run Test", class = "btn-success")
            )
          ),
          column(8,
            box(title = "Test Results", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("test_results"))
            )
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "Interpretation", status = "warning", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("test_interpretation"))
            )
          )
        )
      ),
      
      # PCA Tab
      tabItem(tabName = "pca",
        fluidRow(
          column(12,
            h2("Principal Component Analysis", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(4,
            box(title = "PCA Settings", status = "primary", solidHeader = TRUE, width = NULL,
                checkboxInput("pca_scale", "Scale Variables", value = TRUE),
                numericInput("pca_components", "Number of Components:", value = 5, min = 2, max = 10),
                actionButton("run_pca", "Run PCA", class = "btn-success"),
                br(), br(),
                downloadButton("download_pca", "Download Results", class = "btn-info")
            )
          ),
          column(8,
            box(title = "PCA Results", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(plotOutput("pca_plot", height = "400px"))
            )
          )
        ),
        
        fluidRow(
          column(6,
            box(title = "Eigenvalues", status = "success", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("pca_eigenvalues"))
            )
          ),
          column(6,
            box(title = "Variable Contributions", status = "warning", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("pca_contributions"))
            )
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "PCA Interpretation", status = "primary", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("pca_interpretation"))
            )
          )
        )
      ),
      
      # Cluster Analysis Tab
      tabItem(tabName = "cluster",
        fluidRow(
          column(12,
            h2("Cluster Analysis", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(4,
            box(title = "Clustering Settings", status = "primary", solidHeader = TRUE, width = NULL,
                selectInput("cluster_method", "Method:",
                           choices = c("K-Means" = "kmeans", "Hierarchical" = "hierarchical")),
                numericInput("cluster_k", "Number of Clusters:", value = 3, min = 2, max = 8),
                actionButton("run_cluster", "Run Clustering", class = "btn-success"),
                br(), br(),
                downloadButton("download_cluster", "Download Results", class = "btn-info")
            )
          ),
          column(8,
            box(title = "Cluster Visualization", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(plotOutput("cluster_plot", height = "400px"))
            )
          )
        ),
        
        fluidRow(
          column(6,
            box(title = "Cluster Summary", status = "success", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("cluster_summary"))
            )
          ),
          column(6,
            box(title = "Cluster Interpretation", status = "warning", solidHeader = TRUE, width = NULL,
                withSpinner(verbatimTextOutput("cluster_interpretation"))
            )
          )
        )
      ),
      
      # Correlation Analysis Tab
      tabItem(tabName = "correlation",
        fluidRow(
          column(12,
            h2("Correlation Analysis", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(4,
            box(title = "Correlation Settings", status = "primary", solidHeader = TRUE, width = NULL,
                selectInput("corr_method", "Method:",
                           choices = c("Pearson" = "pearson", "Spearman" = "spearman", "Kendall" = "kendall")),
                numericInput("corr_threshold", "Significance Threshold:", value = 0.05, min = 0.01, max = 0.1, step = 0.01),
                actionButton("run_correlation", "Run Analysis", class = "btn-success"),
                br(), br(),
                downloadButton("download_correlation", "Download Matrix", class = "btn-info")
            )
          ),
          column(8,
            box(title = "Correlation Heatmap", status = "info", solidHeader = TRUE, width = NULL,
                withSpinner(plotOutput("correlation_plot", height = "400px"))
            )
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "Correlation Matrix", status = "success", solidHeader = TRUE, width = NULL,
                withSpinner(DT::dataTableOutput("correlation_table"))
            )
          )
        )
      ),
      
      # Reports Tab
      tabItem(tabName = "reports",
        fluidRow(
          column(12,
            h2("Analysis Reports", style = "color: #1e293b; margin-bottom: 20px;")
          )
        ),
        
        fluidRow(
          column(6,
            box(title = "Generate Report", status = "primary", solidHeader = TRUE, width = NULL,
                selectInput("report_type", "Report Type:",
                           choices = c("Complete Analysis" = "complete",
                                     "Exploratory Analysis" = "exploratory",
                                     "Statistical Summary" = "statistical")),
                selectInput("report_format", "Format:",
                           choices = c("PDF" = "pdf", "HTML" = "html", "Word" = "docx")),
                textInput("report_title", "Report Title:", value = "SOVI Analysis Report"),
                downloadButton("generate_report", "Generate Report", class = "btn-success")
            )
          ),
          column(6,
            box(title = "Export Data", status = "info", solidHeader = TRUE, width = NULL,
                h4("Available Datasets:"),
                downloadButton("export_sovi", "Export SOVI Data", class = "btn-info"),
                br(), br(),
                downloadButton("export_distance", "Export Distance Matrix", class = "btn-info"),
                br(), br(),
                downloadButton("export_analysis", "Export Analysis Results", class = "btn-warning"),
                br(), br(),
                h4("Cache Management:"),
                actionButton("clear_cache", "Clear Cache", class = "btn btn-warning", 
                           style = "margin: 5px;"),
                textOutput("cache_status_text")
            )
          )
        ),
        
        fluidRow(
          column(12,
            box(title = "Data Citation", status = "success", solidHeader = TRUE, width = NULL,
                h4("How to Cite This Data:"),
                p("Please cite the original data source when using this dataset in your research:"),
                tags$blockquote(
                  "Social Vulnerability Index (SOVI) Dataset for Indonesian Districts. ",
                  "Available at: https://www.sciencedirect.com/science/article/pii/S2352340921010180"
                ),
                h4("Metadata:"),
                verbatimTextOutput("metadata_info")
            )
          )
        )
      )
    )
  )
)

# Server
server <- function(input, output, session) {
  # Reactive values
  values <- reactiveValues(
    sovi_data = NULL,
    distance_data = NULL,
    pca_result = NULL,
    cluster_result = NULL,
    correlation_result = NULL
  )
  
  # Load data on startup (optimized)
  observe({
    # Load SOVI data dengan caching (lebih cepat)
    values$sovi_data <- load_data_with_progress(session)
    
    # Distance matrix di-load on-demand (tidak saat startup)
    values$distance_data <- NULL
    
    # Update UI elements
    if (!is.null(values$sovi_data)) {
      numeric_vars <- names(values$sovi_data)[sapply(values$sovi_data, is.numeric)]
      
      updateSelectInput(session, "explore_variable", choices = numeric_vars)
      updateSelectInput(session, "norm_variable", choices = numeric_vars)
      updateSelectInput(session, "corr_var1", choices = numeric_vars)
      updateSelectInput(session, "corr_var2", choices = numeric_vars)
      updateSelectInput(session, "ttest_variable", choices = numeric_vars)
      
      # Update data status dengan info cache
      cache_status <- check_cache_status()
      cache_info <- if (cache_status$sovi_cached) " (cached)" else ""
      
      output$data_status <- renderUI({
        div(class = "alert alert-success", style = "margin: 0; padding: 10px; font-size: 12px;",
            paste("Data loaded:", nrow(values$sovi_data), "districts", cache_info)
        )
      })
      
      # Hide loading overlay
      runjs("document.getElementById('loading-overlay').style.display = 'none';")
    } else {
      output$data_status <- renderUI({
        div(class = "alert alert-danger", style = "margin: 0; padding: 10px; font-size: 12px;",
            "Failed to load data"
        )
      })
    }
  })
  
  # Dashboard outputs
  output$total_districts <- renderValueBox({
    valueBox(
      value = if (!is.null(values$sovi_data)) nrow(values$sovi_data) else "Loading...",
      subtitle = "Total Districts",
      icon = icon("map"),
      color = "blue"
    )
  })
  
  output$avg_poverty <- renderValueBox({
    valueBox(
      value = if (!is.null(values$sovi_data)) paste0(round(mean(values$sovi_data$POVERTY, na.rm = TRUE), 1), "%") else "Loading...",
      subtitle = "Average Poverty Rate",
      icon = icon("users"),
      color = "red"
    )
  })
  
  output$avg_population <- renderValueBox({
    valueBox(
      value = if (!is.null(values$sovi_data)) format(round(mean(values$sovi_data$POPULATION, na.rm = TRUE)), big.mark = ",") else "Loading...",
      subtitle = "Average Population",
      icon = icon("home"),
      color = "green"
    )
  })
  
  output$data_completeness <- renderValueBox({
    completeness <- if (!is.null(values$sovi_data)) {
      round((1 - sum(is.na(values$sovi_data)) / (nrow(values$sovi_data) * ncol(values$sovi_data))) * 100, 1)
    } else 0
    
    valueBox(
      value = paste0(completeness, "%"),
      subtitle = "Data Completeness",
      icon = icon("check-circle"),
      color = "yellow"
    )
  })
  
  # Dashboard plots
  output$poverty_dist_plot <- renderPlotly({
    if (is.null(values$sovi_data)) return(NULL)
    
    p <- ggplot(values$sovi_data, aes(x = POVERTY)) +
      geom_histogram(bins = 30, fill = "#3b82f6", alpha = 0.7, color = "white") +
      theme_modern() +
      labs(title = "Distribution of Poverty Rates",
           x = "Poverty Rate (%)",
           y = "Frequency")
    
    ggplotly(p)
  })
  
  output$pop_poverty_plot <- renderPlotly({
    if (is.null(values$sovi_data)) return(NULL)
    
    p <- ggplot(values$sovi_data, aes(x = POPULATION, y = POVERTY)) +
      geom_point(alpha = 0.6, color = "#10b981") +
      geom_smooth(method = "lm", se = TRUE, color = "#ef4444") +
      theme_modern() +
      labs(title = "Population vs Poverty Rate",
           x = "Population",
           y = "Poverty Rate (%)")
    
    ggplotly(p)
  })
  
  output$sovi_map <- renderLeaflet({
    if (is.null(values$sovi_data)) return(NULL)
    
    # Create a simple map (since we don't have coordinates in this dataset)
    leaflet() %>%
      addTiles() %>%
      setView(lng = 118, lat = -2, zoom = 5) %>%
      addMarkers(lng = 118, lat = -2, 
                popup = paste("SOVI Dataset<br>", nrow(values$sovi_data), "districts"))
  })
  
  output$dataset_info <- renderText({
    if (is.null(values$sovi_data)) return("Loading...")
    
    metadata <- get_metadata_info()
    paste(
      "Dataset: ", metadata$title, "\n",
      "Source: ", metadata$source, "\n",
      "Description: ", metadata$description, "\n",
      "Variables: ", ncol(values$sovi_data), "\n",
      "Observations: ", nrow(values$sovi_data), "\n",
      "Missing Values: ", sum(is.na(values$sovi_data))
    )
  })
  
  # Data Overview outputs
  output$sovi_table <- DT::renderDataTable({
    if (is.null(values$sovi_data)) return(NULL)
    create_beautiful_table(values$sovi_data, "SOVI Dataset")
  })
  
  output$variable_descriptions <- DT::renderDataTable({
    metadata <- get_metadata_info()
    var_df <- data.frame(
      Variable = names(metadata$variables),
      Description = unlist(metadata$variables),
      stringsAsFactors = FALSE
    )
    create_beautiful_table(var_df, "Variable Descriptions")
  })
  
  output$summary_stats <- DT::renderDataTable({
    if (is.null(values$sovi_data)) return(NULL)
    summary_data <- comprehensive_summary(values$sovi_data)
    create_beautiful_table(summary_data, "Summary Statistics")
  })
  
  # Exploration outputs
  output$exploration_plot <- renderPlotly({
    if (is.null(values$sovi_data) || is.null(input$explore_variable)) return(NULL)
    
    data <- values$sovi_data
    var_name <- input$explore_variable
    
    if (input$plot_type == "histogram") {
      p <- ggplot(data, aes_string(x = var_name)) +
        geom_histogram(bins = 30, fill = "#3b82f6", alpha = 0.7, color = "white") +
        theme_modern() +
        labs(title = paste("Histogram of", var_name), x = var_name, y = "Frequency")
    } else if (input$plot_type == "boxplot") {
      p <- ggplot(data, aes_string(y = var_name)) +
        geom_boxplot(fill = "#10b981", alpha = 0.7, outlier.color = if(input$show_outliers) "red" else NA) +
        theme_modern() +
        labs(title = paste("Box Plot of", var_name), y = var_name)
    } else if (input$plot_type == "density") {
      p <- ggplot(data, aes_string(x = var_name)) +
        geom_density(fill = "#f59e0b", alpha = 0.7) +
        theme_modern() +
        labs(title = paste("Density Plot of", var_name), x = var_name, y = "Density")
    } else if (input$plot_type == "violin") {
      p <- ggplot(data, aes_string(x = '""', y = var_name)) +
        geom_violin(fill = "#8b5cf6", alpha = 0.7) +
        theme_modern() +
        labs(title = paste("Violin Plot of", var_name), x = "", y = var_name)
    }
    
    ggplotly(p)
  })
  
  output$variable_summary <- renderText({
    if (is.null(values$sovi_data) || is.null(input$explore_variable)) return("")
    
    var_data <- values$sovi_data[[input$explore_variable]]
    paste(
      "Variable: ", input$explore_variable, "\n",
      "Mean: ", round(mean(var_data, na.rm = TRUE), 3), "\n",
      "Median: ", round(median(var_data, na.rm = TRUE), 3), "\n",
      "Standard Deviation: ", round(sd(var_data, na.rm = TRUE), 3), "\n",
      "Min: ", round(min(var_data, na.rm = TRUE), 3), "\n",
      "Max: ", round(max(var_data, na.rm = TRUE), 3), "\n",
      "Missing Values: ", sum(is.na(var_data)), "\n",
      "Skewness: ", round(e1071::skewness(var_data, na.rm = TRUE), 3), "\n",
      "Kurtosis: ", round(e1071::kurtosis(var_data, na.rm = TRUE), 3)
    )
  })
  
  # Statistical Analysis
  test_result <- eventReactive(input$run_test, {
    if (is.null(values$sovi_data)) return(NULL)
    
    if (input$test_type == "normality") {
      var_data <- values$sovi_data[[input$norm_variable]]
      if (length(var_data) <= 5000) {
        shapiro.test(var_data)
      } else {
        ks.test(var_data, "pnorm", mean(var_data, na.rm = TRUE), sd(var_data, na.rm = TRUE))
      }
    } else if (input$test_type == "correlation") {
      cor.test(values$sovi_data[[input$corr_var1]], values$sovi_data[[input$corr_var2]])
    } else if (input$test_type == "ttest") {
      t.test(values$sovi_data[[input$ttest_variable]], mu = input$ttest_mu)
    }
  })
  
  output$test_results <- renderText({
    result <- test_result()
    if (is.null(result)) return("")
    
    if (input$test_type == "normality") {
      paste("Normality Test Results:\n",
            "Statistic: ", round(result$statistic, 4), "\n",
            "P-value: ", round(result$p.value, 4), "\n",
            "Method: ", result$method)
    } else if (input$test_type == "correlation") {
      paste("Correlation Test Results:\n",
            "Correlation: ", round(result$estimate, 4), "\n",
            "P-value: ", round(result$p.value, 4), "\n",
            "95% CI: [", round(result$conf.int[1], 4), ", ", round(result$conf.int[2], 4), "]")
    } else if (input$test_type == "ttest") {
      paste("One-Sample T-Test Results:\n",
            "T-statistic: ", round(result$statistic, 4), "\n",
            "P-value: ", round(result$p.value, 4), "\n",
            "Mean: ", round(result$estimate, 4), "\n",
            "95% CI: [", round(result$conf.int[1], 4), ", ", round(result$conf.int[2], 4), "]")
    }
  })
  
  output$test_interpretation <- renderText({
    result <- test_result()
    if (is.null(result)) return("")
    
    if (input$test_type == "normality") {
      if (result$p.value > 0.05) {
        "Interpretation: Data appears to be normally distributed (p > 0.05)"
      } else {
        "Interpretation: Data does not appear to be normally distributed (p â‰¤ 0.05)"
      }
    } else if (input$test_type == "correlation") {
      if (result$p.value > 0.05) {
        "Interpretation: No significant correlation between variables (p > 0.05)"
      } else {
        strength <- if (abs(result$estimate) > 0.7) "strong" else if (abs(result$estimate) > 0.3) "moderate" else "weak"
        direction <- if (result$estimate > 0) "positive" else "negative"
        paste("Interpretation: Significant", strength, direction, "correlation (p â‰¤ 0.05)")
      }
    } else if (input$test_type == "ttest") {
      if (result$p.value > 0.05) {
        paste("Interpretation: No significant difference from", input$ttest_mu, "(p > 0.05)")
      } else {
        paste("Interpretation: Significant difference from", input$ttest_mu, "(p â‰¤ 0.05)")
      }
    }
  })
  
  # PCA Analysis
  pca_result <- eventReactive(input$run_pca, {
    if (is.null(values$sovi_data)) return(NULL)
    perform_pca(values$sovi_data, scale = input$pca_scale)
  })
  
  output$pca_plot <- renderPlot({
    result <- pca_result()
    if (is.null(result)) return(NULL)
    create_pca_plot(result, values$sovi_data)
  })
  
  output$pca_eigenvalues <- DT::renderDataTable({
    result <- pca_result()
    if (is.null(result)) return(NULL)
    
    eig_df <- data.frame(
      Component = paste0("PC", 1:nrow(result$eig)),
      Eigenvalue = result$eig[,1],
      Variance_Percent = result$eig[,2],
      Cumulative_Percent = result$eig[,3]
    )
    create_beautiful_table(eig_df, "PCA Eigenvalues")
  })
  
  output$pca_contributions <- DT::renderDataTable({
    result <- pca_result()
    if (is.null(result)) return(NULL)
    
    contrib_df <- as.data.frame(result$var$contrib[, 1:min(5, ncol(result$var$contrib))])
    contrib_df$Variable <- rownames(contrib_df)
    contrib_df <- contrib_df[, c("Variable", setdiff(names(contrib_df), "Variable"))]
    
    create_beautiful_table(contrib_df, "Variable Contributions")
  })
  
  output$pca_interpretation <- renderText({
    result <- pca_result()
    if (is.null(result)) return("")
    interpret_pca(result)
  })
  
  # Cluster Analysis
  cluster_result <- eventReactive(input$run_cluster, {
    if (is.null(values$sovi_data)) return(NULL)
    perform_clustering(values$sovi_data, k = input$cluster_k, method = input$cluster_method)
  })
  
  output$cluster_plot <- renderPlot({
    result <- cluster_result()
    if (is.null(result)) return(NULL)
    create_cluster_plot(result, values$sovi_data)
  })
  
  output$cluster_summary <- DT::renderDataTable({
    result <- cluster_result()
    if (is.null(result)) return(NULL)
    
    if ("cluster" %in% names(result)) {
      cluster_sizes <- table(result$cluster)
      summary_df <- data.frame(
        Cluster = names(cluster_sizes),
        Size = as.numeric(cluster_sizes),
        Percentage = round(as.numeric(cluster_sizes) / sum(cluster_sizes) * 100, 1)
      )
    } else {
      cluster_sizes <- table(result$cluster)
      summary_df <- data.frame(
        Cluster = names(cluster_sizes),
        Size = as.numeric(cluster_sizes),
        Percentage = round(as.numeric(cluster_sizes) / sum(cluster_sizes) * 100, 1)
      )
    }
    
    create_beautiful_table(summary_df, "Cluster Summary")
  })
  
  output$cluster_interpretation <- renderText({
    result <- cluster_result()
    if (is.null(result)) return("")
    interpret_clustering(result, input$cluster_k)
  })
  
  # Correlation Analysis
  correlation_result <- eventReactive(input$run_correlation, {
    if (is.null(values$sovi_data)) return(NULL)
    perform_correlation(values$sovi_data, method = input$corr_method)
  })
  
  output$correlation_plot <- renderPlot({
    result <- correlation_result()
    if (is.null(result)) return(NULL)
    create_correlation_plot(result)
  })
  
  output$correlation_table <- DT::renderDataTable({
    result <- correlation_result()
    if (is.null(result)) return(NULL)
    
    cor_df <- as.data.frame(result)
    cor_df$Variable <- rownames(cor_df)
    cor_df <- cor_df[, c("Variable", setdiff(names(cor_df), "Variable"))]
    
    create_beautiful_table(cor_df, "Correlation Matrix")
  })
  
  # Download handlers
  output$download_plot <- downloadHandler(
    filename = function() {
      paste0("sovi_plot_", input$explore_variable, "_", Sys.Date(), ".png")
    },
    content = function(file) {
      ggsave(file, plot = last_plot(), width = 10, height = 8, dpi = 300)
    }
  )
  
  output$export_sovi <- downloadHandler(
    filename = function() { paste0("sovi_data_", Sys.Date(), ".csv") },
    content = function(file) {
      write.csv(values$sovi_data, file, row.names = FALSE)
    }
  )
  
  output$export_distance <- downloadHandler(
    filename = function() { paste0("distance_matrix_", Sys.Date(), ".csv") },
    content = function(file) {
      # Lazy loading distance matrix dengan progress
      if (is.null(values$distance_data)) {
        showNotification("Loading distance matrix (4.2 MB)...", 
                        type = "message", duration = 3)
        
        withProgress(message = 'Preparing distance matrix...', value = 0, {
          incProgress(0.5, detail = "Downloading data...")
          values$distance_data <- load_distance_data_lazy()
          incProgress(1, detail = "Complete!")
        })
        
        if (!is.null(values$distance_data)) {
          showNotification("Distance matrix loaded successfully!", 
                          type = "message", duration = 2)
        } else {
          showNotification("Failed to load distance matrix!", 
                          type = "error", duration = 5)
          return()
        }
      }
      
      write.csv(values$distance_data, file, row.names = FALSE)
    }
  )
  
  output$metadata_info <- renderText({
    metadata <- get_metadata_info()
    cache_status <- check_cache_status()
    
    cache_info <- paste(
      "Cache Status:",
      paste("- SOVI Data:", ifelse(cache_status$sovi_cached, "Cached âœ“", "Not cached")),
      paste("- Distance Matrix:", ifelse(cache_status$distance_cached, "Cached âœ“", "Not cached")),
      paste("- Cache Size:", round(cache_status$cache_size / 1024 / 1024, 2), "MB"),
      sep = "\n"
    )
    
    paste(
      "Title: ", metadata$title, "\n",
      "Source: ", metadata$source, "\n",
      "Description: ", metadata$description, "\n",
      "Variables: ", length(metadata$variables), "\n",
      "Total Districts: ", metadata$total_districts, "\n",
      "Data Sizes: SOVI (", metadata$data_size$sovi, "), Distance (", metadata$data_size$distance, ")", "\n\n",
      cache_info
    )
  })
  
  # Cache management
  observeEvent(input$clear_cache, {
    result <- clear_cache()
    if (result) {
      values$distance_data <- NULL
      showNotification("Cache cleared successfully!", type = "message", duration = 3)
    } else {
      showNotification("No cache to clear!", type = "warning", duration = 3)
    }
  })
  
  output$cache_status_text <- renderText({
    cache_status <- check_cache_status()
    paste("Cache size:", round(cache_status$cache_size / 1024 / 1024, 2), "MB")
  })
}

# Run the application
shinyApp(ui = ui, server = server)

